Are we living in a depressive society?

### 2024-04-04 outputs/paper/paper.qmd
commit

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-ageandtrend-graph
#| fig-cap: "Depressive Disorder Trend by Population Subgroup by Age"

@@

# Plotting the line graph
graph_A <- ggplot(filtered_data, aes(x = Date, y = Value, color = Subgroup)) +
  geom_line(size = 0.4) +
  geom_hline(yintercept = seq(0, 50, by = 10), color = "lightgrey") +
  geom_text(data = label_data,
            aes(label = Subgroup, y = Value + 2), hjust = 1.1, size = 3) +
  scale_y_continuous(name = "Syptom Rates (%)") +
  scale_x_date(date_breaks = "4 months", date_labels = "%Y-%m-%d") +
  labs(title = "Trend of Depressive Disorder Symptoms by Age Group",
       x = NULL,
       y = "Symptom Rates (%)") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = -45, hjust = 1),
        plot.title = element_text(size = 10),
        legend.position = "none")

>>>>

```{r}
# Load necessary libraries
library(tidyverse)
library(lubridate)
library(ggrepel)  # Ensure this package is installed for geom_text_repel

@@

# Plotting the line graph with labels
graph_A <- ggplot(filtered_data, aes(x = Date, y = Value, color = Subgroup)) +
  geom_line(size = 0.4) +
  geom_hline(yintercept = seq(0, 50, by = 10), color = "lightgrey") +
  geom_text_repel(
    data = label_data,
    aes(label = Subgroup),
    nudge_y = 2,
    direction = "y",
    size = 3
  ) +
  scale_y_continuous(name = "Symptom Rates (%)") +
  scale_x_date(date_breaks = "4 months", date_labels = "%Y-%m-%d") +
  labs(title = "Trend of Depressive Disorder Symptoms by Age Group",
       x = NULL,
       y = "Symptom Rates (%)") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = -45, hjust = 1),
        plot.title = element_text(size = 10),
        legend.position = "none")
